---
title: "Practical Machine Learning Project"
author: "Pareel Amre"

This is my submission for Practical Machine Learning Project.
I have used th concepts studied in this course to for this submission.

Building a prediction model to know how a certain user lifts weights based on data obtained from accelerometer.

The dataset consists on 5 classes:

. The subject is lifting weights exactly according to the specification (Class A).

. Throwing the elbow to the front (Class B).

. Lifting the dumbbell only halfway (Class C).

. Lowering the dumbbell only halfway (Class D).

. Throwing the hips to the front (Class E).


```{r,warning=FALSE,message=FALSE,include=FALSE,echo=FALSE}
library(dplyr)
library(ggplot2)
library(DT)
library(caret)
library(knitr)
library(corrplot)
library(plotly)
library(correlationfunnel)
library(GGally)
library(e1071)
#library(rattle)
```


```{r}
files <- read.csv("pml-training.csv", stringsAsFactors = F,na.strings = c("","NA","#DIV/0!"))
second_files <- read.csv("pml-testing.csv", stringsAsFactors = F,na.strings = c("","NA","#DIV/0!"))
```

```{r}
partitions <- createDatapartitions(files$classe, p = 0.8, list = F)
reg <- files[-partitions,]
files <- files[partitions,]
```

```{r}
b_mm <- sapply(select(files,names(files)[grepl("_belt",names(files))]),
                    function(x) sum(is.na(x)))
```
```{r}
arm_mm <- sapply(select(files,names(files)[grepl("_arm",names(files))]),
                   function(x) sum(is.na(x)))
```
```{r}
f_mm <- sapply(select(files,
                              names(files)[grepl("_forearm",names(files))]),
                       function(x) sum(is.na(x)))
```

```{r}
dumb_mmmmmm <- sapply(select(files,
                               names(files)[grepl("_dumbbell",names(files))]),
                        function(x) sum(is.na(x)))
```

```{r}
c_d <- c(names(b_mm[b_mm != 0]), 
                  names(arm_mm[arm_mm != 0]),
                  names(f_mm[f_mm != 0]),
                  names(dumb_mmmmmm[dumb_mmmmmm != 0]))
```
```{r}
a_n_d <- tbl_df(files %>% 
                      select(-c_d,
                             -c(X,user_name, raw_timestamp_part_1, 
                                raw_timestamp_part_2, cvtd_timestamp, 
                                new_window,num_window)))
a_n_d$classe <- as.factor(a_n_d$classe)
a_n_d[,1:52] <- lapply(a_n_d[,1:52],as.numeric)
```

```{r,fig.height=10,fig.width=10}
craasd <- cor(select(a_n_d, -classe))
diag(craasd) <- 0
craasd <- which(abs(craasd)>0.8,arr.ind = T)
craasd <- unique(row.names(craasd))
corrplot(cor(select(a_n_d,craasd)),
         type="upper", order="hclust",method = "number")
```

```{r}
# binarizing data
#correlationfunnel website: https://business-science.github.io/correlationfunnel/
cfun_data <- a_n_d %>% binarize(n_bins = 4, thresh_infreq = 0.01)
```



```{r,fig.align="center",fig.width=8,fig.height=10}
correelaation_asd <- cfun_data %>% correlate(target = classe__A) 
correelaation_asd %>% plot_correlation_funnel(interactive = T,limits = c(-0.5,0.5))
```



```{r, echo=FALSE, eval=FALSE}
temporary_asr <- head(correelaation_asd %>% mutate(corr = abs(correlation)) %>% 
  arrange(desc(corr)) %>% select(feature) %>% unique(),20)
temporary_asr$feature[which(temporary_asr$feature %in% craasd)]
```


```{r,fig.align="center",fig.width=8,fig.height=10}
correaa_basd <- cfun_data %>% correlate(target = classe__B)
correaa_basd %>% plot_correlation_funnel(interactive = T,limits = c(-0.5,0.5))
```



```{r, echo=FALSE, eval=FALSE}
taexf <- head(correaa_basd %>% mutate(corr = abs(correlation)) %>% 
  arrange(desc(corr)) %>% select(feature) %>% unique(),20)
taexf$feature[which(taexf$feature %in% craasd)]
```

 

```{r,fig.align="center",fig.width=8,fig.height=10}
correasde <- cfun_data %>% correlate(target = classe__C)
correasde %>% plot_correlation_funnel(interactive = T,limits = c(-0.5,0.5))
```

 

```{r, echo=FALSE, eval=FALSE}
tempoaedrc<- head(correasde %>% mutate(corr = abs(correlation)) %>% 
  arrange(desc(corr)) %>% select(feature) %>% unique(),20)
tempoaedrc$feature[which(tempoaedrc$feature %in% craasd)]
```



```{r,fig.align="center",fig.width=8,fig.height=10}
corritmonos <- cfun_data %>% correlate(target = classe__D)
corritmonos %>% plot_correlation_funnel(interactive = T,limits = c(-0.5,0.5))
```

  

```{r, echo=FALSE, eval=FALSE}
teanaekdak <- head(corritmonos %>% mutate(corr = abs(correlation)) %>% 
  arrange(desc(corr)) %>% select(feature) %>% unique(),20)
teanaekdak$feature[which(teanaekdak$feature %in% craasd)]
```



```{r,fig.align="center",fig.width=8,fig.height=10}
curote_eae <- cfun_data %>% correlate(target = classe__E)
curote_eae %>% plot_correlation_funnel(interactive = T,limits = c(-0.5,0.5))
```
 

```{r, echo=FALSE, eval=FALSE}
tesraeeaee <- head(curote_eae %>% mutate(corr = abs(correlation)) %>% 
  arrange(desc(corr)) %>% select(feature) %>% unique(),20)
tesraeeaee$feature[which(tesraeeaee$feature %in% craasd)]
```


```{r}
#subseting a_n_d
collumo_asr <- c("magnet_arm_x", "pitch_forearm" , "magnet_dumbbell_y", 
           "roll_forearm", "gyros_dumbbell_y") 
collumo_bsr <- c("magnet_dumbbell_y", "magnet_dumbbell_x" , "roll_dumbbell" , 
           "magnet_belt_y" , "accel_dumbbell_x" )
collumo_csr <- c("magnet_dumbbell_y", "roll_dumbbell" , "accel_dumbbell_y" , 
           "magnet_dumbbell_x", "magnet_dumbbell_z")
collumo_dsr <- c("pitch_forearm" , "magnet_arm_y" , "magnet_forearm_x",
           "accel_dumbbell_y", "accel_forearm_x")
collumo_esr <- c("magnet_belt_y" , "magnet_belt_z" , "roll_belt", 
           "gyros_belt_z" , "magnet_dumbbell_y")
fianslasasas <- character()
for(c in c(collumo_asr,collumo_bsr,collumo_csr,collumo_dsr,collumo_esr)){
  fianslasasas <- union(fianslasasas, c)
}
a_n_d2 <- a_n_d %>% select(fianslasasas, classe)
data.frame("arm" = sum(grepl("_arm",fianslasasas)), 
           "forearm" = sum(grepl("_forearm",fianslasasas)),
           "belt" = sum(grepl("_belt",fianslasasas)),
           "dumbbell" = sum(grepl("_dumbbell",fianslasasas)))
```

 

```{r, fig.align="center",fig.height=15,fig.width=15}
dineermera <- function(data, mapping, ...) {
  ggplot(data = data, mapping=mapping) +
    geom_density(..., alpha = 0.3)+scale_fill_brewer(palette="Set2") 
}
p_dineermera <- function(data, mapping, ...) {
  ggplot(data = data, mapping=mapping) +
    geom_point(..., alpha = 0.1)+ scale_fill_brewer(palette="Set2") 
}
ggpairs(a_n_d2, columns = 1:5,aes(color = classe),
        lower = list(continuous = p_dineermera),diag = list(continuous = dineermera))
```

```{r,fig.align="center",fig.height=15,fig.width=15}
ggpairs(a_n_d2, columns = 6:10,aes(color = classe),
        lower = list(continuous = p_dineermera),diag = list(continuous = dineermera))
```

```{r,fig.align="center",fig.height=15,fig.width=15}
ggpairs(a_n_d2, columns = 11:17,aes(color = classe),
        lower = list(continuous = p_dineermera),diag = list(continuous = dineermera))
```


